The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
use footnotes for all URL refs
Another two questions


git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@139 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also note that some bloggers in the developer community, see
e.g.~\cite{sunsetonmvc}, is currently predicting a paradigm shift in
common practices, prompted by the trend towards richer clients. This
has caused a departure from the time-tested Model-View-Controller
pattern that has been the dominant paradigm in web development for
more than a decade.

@@

As noted in \cite{sunsetonmvc}, AtomPub has a single service endpoint,
and you can navigate to what you need from there. This motivates the
first discussion topic of this paper:

@@

>>>>

We also note that some bloggers in the developer community, see
e.g. a post by Gregg
Caines\footnote{\url{http://caines.ca/blog/programming/the-sun-is-setting-on-rails-style-mvc-frameworks/}},
%\cite{sunsetonmvc} 
is currently predicting a paradigm shift in common practices, prompted
by the trend towards richer clients. This has caused a departure from
the time-tested Model-View-Controller pattern that has been the
dominant paradigm in web development for more than a decade.

@@

%As noted in \cite{sunsetonmvc} 
AtomPub has a single service endpoint,
and you can navigate to what you need from there. This motivates the
first discussion topic of this paper:

@@

\begin{question}
Should the SPARQL 1.1 Graph Store HTTP Protocol be replaced by a
vocabulary like the above?
\end{question}

\begin{question}
Can we create a better vocabulary for hypermedia RDF than the sketch above?
\end{question}
